Combining checkpointing and data compression\\ for high frequency seismic imaging

### 2018-10-04 paper/paper.tex
Version sent to coauthors

\begin{figure*}
\begin{center}
\input{dataflow}
\end{center}
\caption{The dataflow pattern that is typical of adjoint-based optimization problems}
\label{fig:dataflow}
\end{figure*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{images/varying-memory.pdf}
\end{center}
\caption{The speedups predicted by the performance model for varying
  memory. The baseline
(1.0) is the performance of a Revolve-only implementation under the
same conditions. The dotted curve represents the hypothetical speedup
if ZFP supported parallel decompression. The two vertical lines at 20GB and 52GB clearly
divide the plot into 3 regions. The left-most region, with less than
20GB memory sees the maximum benefit from compression. The middle
region, with memory between 20GB and 52GB, is better off using only
Revolve and no compression. The right-most region, with memory greater
than 52GB represents the scenario where the entire history of the
wavefield can fit in memory post-compression. In this case compression
eliminates the use of Revolve - hence the speedup. This is the region
that has been well-studied in past work.}
\label{fig:varying_memory}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\input{dataflow}
\end{center}
\caption{The dataflow pattern that is typical of adjoint-based optimization problems}
\label{fig:dataflow}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{images/varying-memory.pdf}
\end{center}
\caption{The speedups predicted by the performance model for varying
  memory. The baseline
(1.0) is the performance of a Revolve-only implementation under the
same conditions. The different curves represent kernels with differing
compute times (represented here as a factor of the sum of compression
and decompression times). The first vertical line at $~$ 53GB marks the
spot where the compressed wavefield can completely fit in memory and
Revolve is unnecessary if using compression. The second vertical line
at $~$ 2.2 TB marks the spot where the entire uncompressed wavefield can
fit in memory and neither Revolve nor compression is necessary. The
region to the right is where these optimisations are not necessary or
relevant. The middle region has been the subject of past studies using
compression in adjoint problems. The region to the left is the focus
of this paper.}
\label{fig:varying_memory}
\end{figure}
